```{r setup-resources-supplement, include=FALSE}
knitr::opts_chunk$set(results = 'hide', echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra)
```

# Data, code, software and educational materials {#resources-supplement}

I value open science and transparency, so I published my code and data whenever possible. In Table \@ref(tab:tab-resources-chapters), all publicly available resources are listed per chapter.

```{r tab-resources-chapters, results='asis'}
data = read_csv('_bookdown_files/resources-files/table_1_data.csv')
options(knitr.kable.NA = '')
kbl(data, booktabs = T, longtable = T, caption = 'Chapter resources') %>%
    kable_styling(full_width = T, font_size = 8) %>%
    column_spec(column = 1, width = "2.5em") %>%
    column_spec(column = 2, width = "5em") %>%
    column_spec(column = 3, width = "5em") %>%
    footnote(footnote_as_chunk = T, title_format = "italic", threeparttable = T, escape = F, 
             general = 'OpenNeuro repositories contain raw and preprocessed data from individual participants, while NeuroVault contains group-level aggregate data (e.g., statistical brain maps from group-level analyses).')
```

As part of my PhD, I also (co-)developed several courses, which I made publicly accessible. These course materials are listed in Table \@ref(tab:tab-resources-teaching).

```{r tab-resources-teaching, results='asis'}
data = read_csv('_bookdown_files/resources-files/table_2_data.csv')
options(knitr.kable.NA = '')
kbl(data, booktabs = T, longtable = T, caption = 'Teaching resources') %>%
    kable_styling(full_width = T, font_size = 8)
```
